Estimating Neighborhood Rents with Scraped Data

### 2018-06-04 manuscript/index.Rmd
more progress on manuscript

Helena learns where features of are through the user interface (UI) rather than the underlying document object model (DOM). Though the HTML code of a site may regularly change over the course of regular data scraping, websites less frequently undergo drastic overhauls to what their users interact with. Helena also uses skip blocks to avoid re-scraping the an already-collected item. These two aspects of Helena provide its programs robustness to common headaches encountered with web scraping by default. Overall, Helena's programming-by-demonstration method reduces time needed building a scraper from scratch, giving social scientists the capacity to quickly scrape a single table of data or build ongoing data processes.

@@

Figure 3 is a line graphic indicating the Seattle-wide median rent for all sizes of rental units, with the longest set of data (Dupre+Scott) reaching back to 1997 to show long-term dynamics of Seattle rental housing costs. The first takeaway from the graphic is the large spike in rent levels following 2010, with a similar trajectory followed in the estimates from Dupre+Scott and the ACS.

>>>>

Helena learns where features of are through the user interface (UI) rather than the underlying document object model (DOM). Though the HTML code of a site may regularly change over the course of regular data scraping, websites less frequently overhaul what their users actually interact with. Helena also uses skip blocks to avoid re-scraping the an already-collected item. These two aspects of Helena provide its programs robustness to common headaches encountered with web scraping by default. Overall, Helena's programming-by-demonstration method reduces time needed building a scraper from scratch, giving social scientists the capacity to quickly scrape a single table of data or build ongoing data processes.

@@

Figure 3 is a line graphic indicating agreement across data for Seattle-wide median rent (all sizes of rental units). The longest set of data (Dupre+Scott) cover 20 years and show long-term dynamics of Seattle rental housing costs in terms of contract rent. Dupre+Scott released semi-annual summaries for their 20+ unit data, so there are two data points for each year (Spring and Fall). ACS 1-Year Estimates show the median renter-occupied housing unit asking rent. Craigslist shows quarterly estimates for all listings in Seattle.

The first takeaway from the graphic is the large spike in rent levels following 2010, with a similar trajectory followed in the estimates from Dupre+Scott and the ACS. Throughout the span of Dupre+Scott and ACS data, these two indicators differ by about $100-150 at any given point, though the disagreement is at its largest at the ACS data's current endpoint of 2016. Given that the Dupre+Scott data and ACS data both sample rents from already-leased-up units (exclusively in the case of ACS), a plausible explanation for this systematic difference is that Dupre+Scott rent estimates reflect only the population of rental units in larger structures (whereas ACS is theoretically sampling rental units of all property sizes and characteristics.

Only the Craigslist and Dupre+Scott are particularly useful for understanding more recent median levels for the Seattle rental housing market.
